%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.7in}

% \urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ruslan Sakevych} & xlionell@gmail.com\\
  github.com/lionell & 1-650-732-8050\\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Google}{Seattle, WA}
      {Senior Software Engineer}{May 2021 - Present}
      \resumeItemListStart
        \resumeItem{Led the development of a critical service responsible for microarchitecture selection for executables, directly impacting performance and resource utilization for Google-scale systems.}
        \resumeItem{Spearheaded research and prototyping of a Reinforcement Learning solution for the architecture selection problem, demonstrating potential for significant automated optimization.}
        \resumeItem{Directed A/B experimentation efforts that identified and resolved critical non-cross-platform code, improving system-wide compatibility and developer productivity.}
        \resumeItem{Architected and developed neural embeddings for Google's build graph to solve large-scale distance oracle problems and optimize dependency analysis.}
        \resumeItem{Invented a novel online log clustering algorithm that outperformed the state-of-the-art LogParser, enhancing anomaly detection and system monitoring capabilities.}
      \resumeItemListEnd

    \resumeSubheading
      {Facebook}{Seattle, WA}
      {Software Engineer}{Oct 2019 - May 2021}
      \resumeItemListStart
        \resumeItem{Designed and led the implementation of a real-time service for Probabilistic Flakiness Score computation using Bayesian inference, a key component of Facebook's CI pipeline. (See: engineering.fb.com/2020/12/10/developer-tools/probabilistic-flakiness)}
        \resumeItem{Engineered a 10x improvement in CPU utilization and a 20x reduction in latency for the PFS service through advanced profiling, caching, and parallelization techniques.}
        \resumeItem{Pioneered the replacement of a legacy statistical model with a stochastic ML model for sizing CI workflows, resulting in a 30\% reduction in memory utilization and a 17\% decrease in OOM errors.}
        \resumeItem{Researched and prototyped an innovative ML model for CI workflow ETA estimation, achieving a 50\% reduction in MSLE and enabling confidence-level predictions via Monte-Carlo dropout layers.}
      \resumeItemListEnd

    \resumeSubheading
      {Google}{CA, USA}
      {Software Engineering Intern (Four Terms)}{2016 - 2019}
      \resumeItemListStart
        \resumeItem{Spearheaded multiple ML initiatives for build system optimization, including migrating a legacy pipeline to TFX, researching build-time prediction models, and training models to forecast memory usage.}
        \resumeItem{Designed and built a suite of developer tools at Google-scale, including an automated memory regression finder and a troubleshooting dashboard, which led to the identification of major regressions.}
        \resumeItem{Engineered significant performance improvements by implementing a parallel N-ary search algorithm (16x speedup in culprit finding) and designing novel batching strategies to reduce resource consumption.}
      \resumeItemListEnd

    \resumeSubheading
      {Facebook}{London, UK}
      {Software Engineer Intern}{Jan 2018 - Mar 2018}
      \resumeItemListStart
        \resumeItem{Re-architected the Hack language parser to be reactive, achieving a 25\% parse time reduction for the full-codebase type-checker and up to 50\% speedup for fact extraction tools.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Microsoft}{Redmond, WA}
      {Software Developer Intern}{Jul 2017 - Oct 2017}
      \resumeItemListStart
        \resumeItem{Engineered an automated workflow for raw telemetry data aggregation and transformation, used for intermediate metric aggregation to significantly reduce data volumes and accelerate queries.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------SKILLS-----------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Areas of Expertise}
      {Machine Learning (Deep Learning, NLP, Reinforcement Learning), Distributed Systems, CI/CD Infrastructure, Compilers, Performance Optimization, A/B Testing}
    \resumeSubItem{Languages \& Frameworks}
      {Python (PyTorch, TensorFlow/TFX, Scikit-learn), Go, C++, Java, OCaml, SQL, Bash}
    \resumeSubItem{Technologies \& Platforms}
      {Kubernetes, Docker, Google Cloud Platform (GCP), AWS, Apache Spark, Apache Beam, Hadoop, MapReduce, Borg}
 \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, USA}
      {M.S. in Computer Science \& Engineering; GPA: 3.83}{2022 - 2025}
    \resumeSubheading
      {Taras Shevchenko National University}{Kyiv, Ukraine}
      {M.S. in Computer Science; GPA: 3.94}{2018 - 2020}
    \resumeSubheading
      {Taras Shevchenko National University}{Kyiv, Ukraine}
      {B.S. in Computer Science; GPA: 3.98}{2014 - 2018}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}